\section{Expected Outcomes}
From the discussed methodology, the following are what are expected from this project :
\subsection{Discharge flow control}
A discharge flow control control mechanism that can turn the ball valve in precise steps is expected. The steps obtained from the division of the circumference of a full turn by the number of steps are also expected to be accurate to the nearest whole number.
\subsection{Discharge collection unit}
A discharge collection unit that can precisely collect the discharge within the specified time interval while taking its temperature and weight is expected. This can be expected if the expectations of the following sub-units are met :
\subsubsection{Flow diversion sub-unit}
A precisely sized diversion sub-unit, correctly positioned to collect the whole stream is expected. This will improve on the accuracy of the weight of the discharge and hence that of the experiment.
\subsubsection{Discharge collection tank}
A discharge collection tank whose shape can allow for accurate weight measurement is expected. It is also expected that this tank is positioned in such a way that flow into this tank utilizes gravity to eliminate the need for an extra pump.
\subsubsection{Outlet valve}
A sized outlet valve positioned at a point on the tank that it empties the tank the fastest way possible is expected. 
\subsection{Discharge weight and temperature measurements}
It is expected these units measuring devices can measure to the smallest resolution.

\subsection{Control and Display}
It is expected that the control module can handle intense computations such as error approximation, immediate rendering of results and communicating with the sensors and transducers that will be used in the system. It is also expected that the user interface is slick and ergonomic.





